Constructing Biological Regulatory Networks from Process Hitting models

### 2013-07-30 main.tex
abstract

On the other hand, the qualitative modeling of BRNs has been widely addressed using Ren\'e Thomas'
formalism, leading to numerous theoretical work and practical tools to understand emerging behaviors.
In addition to be able to use the existing results on this formalism,
obtaining the Thomas representation of a PH model allows the iteratively refine a system.

>>>>

On the other hand, the qualitative modeling of BRNs has been widely addressed using Ren\'e Thomas'
formalism, leading to numerous theoretical work and practical tools to understand emerging behaviors.
%In addition to be able to use the existing results on this formalism,
%obtaining the Thomas representation of a PH model allows to iteratively refine a model.
Linking this representation to PH would not only allow to use the existing results on this formalism,
but also to iteratively refine the model of a system.
